# LINCS

This is LINCS

## Signatures

Putative drug therapies were identified with signature-based connectivity analysis utilizing the Library of Integrated Network-based Signatures (LINCS) database.

```{r lincs-signatures, results='asis'}

global_state$data <- global_state$data %>%
  purrr::map(function(x) {
    
    signature <- x$data
    
    # If we don't have human datam, convert mouse or rat genes to human orthologs for iLINCS
    if(global_state$species != "human") { 
      orthologs <- babelgene::orthologs(genes = signature$Symbol, 
                                        human = FALSE, 
                                        species = global_state$species) %>%
        dplyr::select(Symbol = human_symbol, Symbol_old = symbol)
      
      signature <- signature %>%
        dplyr::rename(Symbol_old = Symbol) %>%
        dplyr::inner_join(orthologs, by = "Symbol_old") %>%
        dplyr::select(-Symbol_old)
    }
    
    # Run iLINCS on our signature
    signatures <- drugfindR::investigateSignature(
      expr = signature,
      filterThreshold = 0,
      similarityThreshold = 0.2,
      outputLib = "CP",
      geneColumn = "Symbol",
      logfcColumn = "log2FoldChange",
      pvalColumn = "pvalue")
    
    # Split the signatures then annotate with perturbagen metadata
    concordant <- signatures %>%
      dplyr::filter(Similarity >= 0) %>% 
      dplyr::inner_join(get_ilincs_metadata(.$TargetSignature), by = "TargetSignature") %>%
      left_join(global_state$lincs_fda, by = c("Target" = "sm_name"))
    
    discordant <- signatures %>%
      dplyr::filter(Similarity < 0) %>% 
      dplyr::inner_join(get_ilincs_metadata(.$TargetSignature), by = "TargetSignature") %>%
      dplyr::left_join(global_state$lincs_fda, by = c("Target" = "sm_name"))
    
    # Summarize and count unique MOAs
    concordant_moa_report <- generate_moa_report(concordant)
    discordant_moa_report <- generate_moa_report(discordant)
    
    # Summarize and count unique Gene Targets
    concordant_gene_report <- generate_gene_report(concordant, signature)
    discordant_gene_report <- generate_gene_report(discordant, signature)
    
    # Do enrichR with the gene targets
    discordant_pathways <- do_enrichr(discordant_gene_report$Symbol) 
    concordant_pathways <- do_enrichr(concordant_gene_report$Symbol)
    
    # Package together to store in results
    lincs <- dplyr::lst(concordant,
      discordant,
      concordant_moa_report,
      discordant_moa_report,
      concordant_gene_report,
      discordant_gene_report,
      discordant_pathways,
      concordant_pathways)
    
    x$results$lincs <- lincs
    
    x
})

global_state$data %>%
  purrr::map(~ knitr::knit_child(here::here("Rmd", "lincs_signatures.Rmd"), 
                                 envir = environment(), 
                                 quiet = TRUE)) %>%
  purrr::list_c() %>%
  cat(sep = "\n")
```

## MOAS and Genes

These are LINCS Perturbagens MoAs and Genetargets

```{r lincs-moas-genes, results='asis'}
global_state$data %>%
  purrr::map(~ knitr::knit_child(here::here("Rmd", "lincs_metadata.Rmd"), 
                                 envir = environment(), 
                                 quiet = TRUE)) %>%
  purrr::list_c() %>%
  cat(sep = "\n")
```

## Pathways

These are LINCS Pathways

```{r lincs-pathways, results='asis'}
global_state$data %>%
  purrr::map(~ knitr::knit_child(here::here("Rmd", "lincs_pathways.Rmd"), envir = environment(), quiet = TRUE)) %>%
  purrr::list_c() %>%
  cat(sep = "\n")
```

## PAVER

These are PAVER plots of the pathways from all comparisons

```{r lincs-paver, results='asis'}
lincs_paver_input <- purrr::map_dfr(global_state$data, function(x) {
  dplyr::bind_rows(
    x$results$lincs$concordant_pathways,
    x$results$lincs$discordant_pathways %>% dplyr::mutate(Combined.Score = Combined.Score * -1)
  )
}, .id = "Group") %>%
  dplyr::select(GOID, CS = Combined.Score, Group) %>%
  dplyr::mutate(CS = sign(CS) * log2(abs(CS)) + 1,
         Type = ifelse(CS > 0, "C", "D")) %>%
  dplyr::distinct(GOID, Group, .keep_all = TRUE) %>%
  tidyr::pivot_wider(names_from = c(Group, Type), values_from = CS, names_sep = "-")

minClusterSize = 5
maxCoreScatter = 0.33
minGap = (1 - maxCoreScatter) * 3 / 4

LINCS_PAVER_result <- PAVER::prepare_data(lincs_paver_input, global_state$embeddings, global_state$term2name) %>%
  PAVER::generate_themes(maxCoreScatter = maxCoreScatter, minGap = minGap, minClusterSize = minClusterSize)

global_state$results <- append(global_state$results, dplyr::lst(LINCS_PAVER_result))

list(LINCS_PAVER_result, "logCS") %>%
  knitr::knit_child(text = readLines(here::here("Rmd", "paver_report.Rmd")),
             envir = environment(),
             quiet = TRUE) %>%
  cat(sep = "\n")
```
