# Pods

These are all possible overlaps of pathways across all possible comparisons.

```{r pods-upset}
upset_plot = global_state$results %>%
  purrr::map_dfr("prepared_data", .id = "Pod") %>%
  dplyr::mutate(Pod = stringr::word(Pod, sep =  "_"),
                Group = stringr::str_remove(Group, "-C|-D"),
                ID = paste0(Group, "_", Pod)) %>%
  dplyr::select(ID, GOID) %>%
  dplyr::group_by(GOID) %>%
  dplyr::summarise(ID = list(ID)) %>%
  dplyr::filter(!stringr::str_detect(ID, "LINCS") | stringr::str_detect(ID, "GSEA|Enrichr")) %>% 
  ggplot2::ggplot(aes(x = ID)) +
  ggplot2::geom_bar() +
  ggprism::theme_prism(base_size = 9) + 
  ggupset::scale_x_upset() +
  labs(x = NULL, y = "Pathways")

upset_plot

```

## 2nd Pod

These are overlaps between each datasets GSEA and EnrichR results

```{r pods-2pod, results='asis', eval=FALSE, include=FALSE}

# Generate venn diagrams of each comparison's overlap in GSEA and enrichR results
# TODO: this could be cleaner
twopod_plots = global_state$results %>%
  purrr::map_dfr("prepared_data", .id = "Pod") %>%
  dplyr::mutate(Pod = stringr::word(Pod, sep =  "_")) %>%
  dplyr::filter(Pod != "LINCS") %>%
  dplyr::group_by(Group, Pod) %>%
  dplyr::summarise(GOID = list(GOID)) %>%
  dplyr::group_by(Group) %>%
  tidyr::nest() %>%
  with(stats::setNames(purrr::map(data, tibble::deframe), Group)) %>% # whew
  purrr:::map(~ ggVennDiagram::ggVennDiagram(.)) %>% 
  .[order(names(.))]

twopod_data = global_state$results %>%
  purrr::map_dfr("prepared_data", .id = "Pod") %>%
  dplyr::mutate(Pod = stringr::word(Pod, sep =  "_")) %>%
  dplyr::filter(Pod != "LINCS") %>%
  dplyr::mutate(value = ifelse(Pod == "ENRICHR", sign(value) * 2^(abs(value)-1), value)) %>% # Reconstruct combined score from logCS
  dplyr::mutate(Pod = stringr::str_replace(Pod, "ENRICHR", "Enrichr")) %>%
  dplyr::group_by(Group) %>%
  tidyr::nest() %>%
  tibble::deframe() %>%
  purrr::map(function(x){
    
    top10 = x %>%
      dplyr::filter(sign(value) == 1) %>%
      dplyr::group_by(GOID) %>%
      dplyr::filter(dplyr::n() > 1) %>%
      dplyr::ungroup() %>%
      dplyr::select(GOID, Pod, value) %>%
      tidyr::pivot_wider(names_from = "Pod", values_from = "value") %>%
      dplyr::arrange(!!!purrr::map(dplyr::select(., dplyr::where(is.numeric)), ~ dplyr::desc(.x))) %>% # Sort numeric columns in descending order of appearance
      dplyr::inner_join(global_state$term2name) %>%
      dplyr::relocate(Term, .after = GOID)
    
    bot10 = x %>%
      dplyr::filter(sign(value) == -1) %>%
      dplyr::group_by(GOID) %>%
      dplyr::filter(dplyr::n() > 1) %>%
      dplyr::ungroup() %>%
      dplyr::select(GOID, Pod, value) %>%
      tidyr::pivot_wider(names_from = "Pod", values_from = "value") %>%
      dplyr::arrange(!!!purrr::map(dplyr::select(., dplyr::where(is.numeric)), ~ (.x))) %>% # Sort numeric columns in ascending order of appearance
      dplyr::inner_join(global_state$term2name) %>%
      dplyr::relocate(Term, .after = GOID)

    dplyr::lst(`Top 10` = top10, `Bottom 10` = bot10)
      
  }) %>% .[order(names(.))]

global_state$results <- append(global_state$results, dplyr::lst(`twopod_data` = twopod_data))

list(names(twopod_plots) %>% as.list(), 
     twopod_plots, 
     twopod_data) %>%
  purrr::pmap(~ knitr::knit_child(
    text = c(
      '',
      '### `r ..1`',
      '',
      '```{r}',
      'print(..2)',
      'make_table(..3[[1]], caption = \'Shared Upregulated Pathways\')',
      'make_table(..3[[2]], caption = \'Shared Downregulated Pathways\')',
      '```',
      ''
    ), envir = environment(), quiet = TRUE)) %>%
  purrr::list_c() %>%
  cat(sep = "\n")
```

## 3rd Pod

These are overlaps between each datasets GSEA and EnrichR and LINCS results

```{r pods-3pod, results='asis', eval=FALSE, include=FALSE}
threepod_plots = global_state$results %>%
  purrr::map_dfr("prepared_data", .id = "Pod") %>%
  dplyr::mutate(Pod = stringr::word(Pod, sep =  "_"),
                Group = stringr::str_remove(Group, "-C|-D")) %>%
  dplyr::group_by(Group, Pod) %>%
  dplyr::summarise(GOID = list(GOID)) %>%
  dplyr::group_by(Group) %>%
  tidyr::nest() %>%
  with(stats::setNames(purrr::map(data, tibble::deframe), Group)) %>% # whew
  purrr:::map(~ ggVennDiagram::ggVennDiagram(.)) %>% 
  .[order(names(.))]

threepod_data = global_state$results %>%
  purrr::map_dfr("prepared_data", .id = "Pod") %>%
  dplyr::mutate(Pod = stringr::word(Pod, sep =  "_"),
                Group = stringr::str_remove(Group, "-C|-D")) %>%
  dplyr::mutate(value = ifelse(Pod == "ENRICHR" | Pod == "LINCS", sign(value) * 2^(abs(value)-1), value)) %>% # Reconstruct combined score from logCS
  dplyr::mutate(Pod = stringr::str_replace(Pod, "ENRICHR", "Enrichr")) %>%
  dplyr::group_by(Group) %>%
  tidyr::nest() %>%
  tibble::deframe() %>%
  purrr::map(function(x){
    
    top10 = x %>%
      dplyr::filter(sign(value) == 1) %>%
      dplyr::group_by(GOID) %>%
      dplyr::filter(dplyr::n() > 2) %>%
      dplyr::ungroup() %>%
      dplyr::select(GOID, Pod, value) %>%
      tidyr::pivot_wider(names_from = "Pod", values_from = "value") %>%
      dplyr::arrange(!!!purrr::map(dplyr::select(., dplyr::where(is.numeric)), ~ dplyr::desc(.x))) %>% # Sort numeric columns in descending order of appearance
      dplyr::inner_join(global_state$term2name) %>%
      dplyr::relocate(Term, .after = GOID)
    
    bot10 = x %>%
      dplyr::filter(sign(value) == -1) %>%
      dplyr::group_by(GOID) %>%
      dplyr::filter(dplyr::n() > 2) %>%
      dplyr::ungroup() %>%
      dplyr::select(GOID, Pod, value) %>%
      tidyr::pivot_wider(names_from = "Pod", values_from = "value") %>%
      dplyr::arrange(!!!purrr::map(dplyr::select(., dplyr::where(is.numeric)), ~ (.x))) %>% # Sort numeric columns in ascending order of appearance
      dplyr::inner_join(global_state$term2name) %>%
      dplyr::relocate(Term, .after = GOID)

    dplyr::lst(`Top 10` = top10, `Bottom 10` = bot10)
      
  }) %>% .[order(names(.))]

fourpod_data <- threepod_data %>% 
  purrr::map(dplyr::bind_rows) %>%
  purrr::reduce(dplyr::inner_join, by = "Term") %>%
  dplyr::select(GOID = dplyr::first(dplyr::contains("GOID")), Term)

global_state$results <- append(global_state$results, dplyr::lst(`threepod_data` = threepod_data, fourpod_data))

list(names(threepod_plots) %>% as.list(), 
     threepod_plots, 
     threepod_data) %>%
  purrr::pmap(~ knitr::knit_child(
    text = c(
      '',
      '### `r ..1`',
      '',
      '```{r}',
      'print(..2)',
      'make_table(..3[[1]], caption = \'Shared Upregulated Pathways\')',
      'make_table(..3[[2]], caption = \'Shared Downregulated Pathways\')',
      '```',
      ''
    ), envir = environment(), quiet = TRUE)) %>%
  purrr::list_c() %>%
  cat(sep = "\n")
```

<!-- ## 4th Pod -->
```{r pods-4pod, results='asis', eval=FALSE, include=FALSE}
if(nrow(global_state$results$fourpod_data) > 0) {
  global_state$results$fourpod_data %>%
    knitr::knit_child(
    text = c(
      '',
      '## 4th Pod',
      '',
      'These are the overlaps between each 3 datasets 3rd pod.',
      '',
      '```{r}',
      'make_table(.)',
      '```',
      ''), envir = environment(), quiet = TRUE) %>%
    cat(sep = "\n")
}
```
